\textit{Supplemental Figures for}: A Gaussian process model of human electrocorticographic data

### 2018-10-11 paper/supporting_information.tex
figure edits, supp caption edits, recompiled all docs

\begin{figure}[p]
\centering
\includegraphics[width=\textwidth]{figs/supplemental_3}
\caption{\textbf{Reconstruction quality for each experiment.} \textbf{A. \& C.  Distributions
      of correlation coefficients.}  Across all electrodes from all
    patients in the labeled experiment from dataset 2, the panel displays the distribution of correlations between the observed and reconstructed LFP data using models trained on data from all other patients (Across, in black) and all other electrodes from the same patient (Within, in gray). 
    \textbf{B. \& D. Correlation maps.}  The glass brain maps display the
    average correlation between the observed LFP data and the across-subjects model reconstructed data by location, for each labeled experiment.}
\label{fig:supplemental_3}
\end{figure}

\begin{figure}[p]
\centering
\includegraphics[width=\textwidth]{figs/supplemental_4}
\caption{\textbf{Reconstruction accuracy predicted by data
    features for each dataset.} \textbf{A.--F.  Features from Dataset
    1.}  Features include: (\textbf{A.}) number of electrodes,
  (\textbf{B.}) proportion thresholded, (\textbf{C.}), total recording
  time, (\textbf{D.}) number thresholded, (\textbf{E.}) number of
  sessions, and (\textbf{F.}) average session length.  The histograms
  report the distributions of the z-transformed correlation
  coefficients and the associated data feature.
  \textbf{G.--L. Features from Dataset 2.}  Analogous format to Panels
  A--F.}
\label{fig:supplemental_4}
\end{figure}

\begin{figure}[ptb]
\centering
\includegraphics[width=\textwidth]{figs/supplemental_5}
\caption{\textbf{ Top 10\% most informative voxels.}
 Voxels in yellow indicate the intersections between
    the top 10\% most informative voxels in each brain map from Figure
    5, indicated by the white contours.}
\label{fig:supplemental_5}
\end{figure}

>>>>

\begin{figure}[p]
\centering
\includegraphics[width=\textwidth]{figs/supplemental_3}
\caption{\textbf{Reconstruction quality across all electrodes in two
      Dataset 2 experiments.}  \textbf{A. Distributions of correlations
      between observed versus reconstructed activity by electrode, for
      Experiment 1.}  Same format as Figure~3A and B, but reflects data shown
    in Figure~\ref{fig:supplemental_2}A (rightmost violin plot).
 \textbf{B. Distributions of correlations
      between observed versus reconstructed activity by electrode, for
      Experiment 2.}  Same format as Figure~3A and B, but reflects
    data shown in Figure~\ref{fig:supplemental_2}B (rightmost violin
    plot).  \textbf{C.--D.  Reconstruction
      performance by location.} Each dot reflects the location of a
    single implanted electrode from Dataset 2, Experiment 1 (Panel C)
    or Dataset 2, Experiment 2 (Panel D).  The dot colors denote the
    average within-experiment (across-session)
    correlation, using the across-patient correlation model, between
    the observed and reconstructed activity at the given electrode
    location.}
\label{fig:supplemental_3}
\end{figure}

\begin{figure}[p]
\centering
\includegraphics[width=\textwidth]{figs/supplemental_4}
\caption{\textbf{Reconstruction accuracy versus within-subject data
    features for two ECoG datasets.} \textbf{A.--F.  Features from
    Dataset 1.}  Features include: (\textbf{A.}) total number of
  electrodes implanted in each patient's brain, (\textbf{B.})
  per-patient number of electrodes that were filtered out due to
  having an average kurtosis greater than 10, (\textbf{C.})
  per-patient proportion of electrodes that were filtered out due to
  having an average kurtosis greater than 10, (\textbf{D.})
  per-patient number of recording sessions, (\textbf{E.}) per-patient
  total recording time (h), and (\textbf{F.}) per-patient average
  session length (h).  \textbf{G.--L. Features from Dataset 2.}
  Analogous format to Panels A--F.}
\label{fig:supplemental_4}
\end{figure}

\begin{figure}[ptb]
\centering
\includegraphics[width=\textwidth]{figs/supplemental_5}
\caption{\textbf{Most informative electrode locations.}  This map
  shows the region outlined in white from Figure~5 in greater detail.
Across Datasets 1 and 2, electrodes in these locations were identified as yielding the (10\%)
best reconstruction accuracies at \textit{other} locations throughout
the brain.}
\label{fig:supplemental_5}
\end{figure}
